### 2024-04-09 README.qmd
Update with offence types

```{r}
d_offence |>
  count(offence, sort = TRUE) |>
  mutate(percent_records = n / nrow(d_offence)) |>
  mutate(percent_records = scales::percent(percent_records)) |>
  arrange(desc(n)) |>
  head(10) |>
  knitr::kable()
```

>>>>

```{r}
d_all |>
  opsnap:::filter_offence_nas() |>
  filter(offence != "n/a") |>
  count(offence, sort = TRUE) |>
  mutate(percent_records = n / nrow(d_offence)) |>
  mutate(percent_records = scales::percent(percent_records)) |>
  arrange(desc(n)) |>
  head(10) |>
  knitr::kable()
```

The equivalent for cyclists, with the least common offences categorised as 'other', is shown below:

```{r}
d_all |>
  opsnap:::filter_offence_nas() |>
  filter(offence != "n/a") |>
  filter(mode == "cyclist") |>
  count(offence, sort = TRUE) |>
  mutate(percent_records = n / nrow(d_offence)) |>
  mutate(percent_records = scales::percent(percent_records)) |>
  mutate(
    offence = ifelse(n < 20, "other", offence)
  ) |>
  group_by(offence) |>
  summarise(n = sum(n), n_hybrid = n()) |>
  arrange(n_hybrid, desc(n)) |>
  select(-n_hybrid) |>
  mutate(`% of total` = scales::percent(n / sum(n), accuracy = 0.1)) |>
  knitr::kable()
```
